\begin{rubric}{Employment History}
\subrubric{Align Technology}
\entry*[2026 -- Present]%
	\textbf{3D C++ Software Engineer}
 \begin{itemize}
     \item As part of the Bio-Mechanical R\&D group, I work on geometric algorithms for orthodontic CAD software.
 \end{itemize}
\subrubric{GE Vernova}
\entry*[2023 -- 2025]%
	\textbf{Software Engineer, Conceptual Design and Aerodynamics}
    Lead developer of GE's Wind Turbine Conceptual Design Toolchain, based on Python and C++, which included
 \begin{itemize} 
    \item B-spline based geometry manipulation with continuity guarantees for blade aero design. Written in Python, GUI with interactive control points.
    \item Blade structural optimization for blade structural design. Written in C++, optimizes laminate plan for a blade based on given loads.
    \item Loads-structure convergence iterations. Written in Python which combines tools spread across 3 different teams into a single software.
  \end{itemize}
%
% Blank lines result in extra space!
%
\entry*[2021 -- 2023]%
	\textbf{Edison Engineering Development Program} (2 year technical leadership rotational program)
 \begin{itemize}
     \item Developed a steady state aeroelastic code in Python for wind turbine blades by coupling in-house aerodynamics (BEM) and structural (FEM, corotational beam elements) codes.
     \item Developed a FEM mesh manipulation library in C++, based on the Partial Entity data structure for representation of non-manifold edges.
     \item Contributed to the development of an aeroelastic mode tracking module in Python, based on a Modal Assurance Criterion (MAC).
     \item Implemented a critical Python module for improving 50-year extreme load extrapolation on the AWS simulation environment by making the tail of the load distribution denser.
\end{itemize}
\end{rubric}